Resolvable Ambiguity

### 2019-07-09 paper/paper.tex
Small addendum to Orc

\begin{itemize}
\item We could decide to forbid the case where two comparisons are
  right next to each other, e.g., \syncon{forbid gt.left = gt} and
  \syncon{forbid gt.right = gt} (where \syncon{gt} is the syncon
  for the greater-than operator).
\item We could change the definition of the parallel combinators
  and define separate lexical tokens for the combinators, e.g.,
  \syncon{token Seq = ">[[:lower:]][[:word:]]*>"}.
\item We could change the syntax of the combinators completely to
  avoid clashes with other operators.
\end{itemize}

The change in the first alternative can be done after composition,
and would allow us to reuse both language definitions without
modifications. In the latter two alternatives, we lose reuse of
the definitions of Orc combinators, but place no additional
restrictions on the base language. The preferred variant is likely
to differ between different compositions and different languages.

>>>>

\begin{itemize}
\item We could decide to forbid the case where two comparisons are
  right next to each other, e.g., \syncon{forbid gt.left = gt} and
  \syncon{forbid gt.right = gt} (where \syncon{gt} is the syncon
  for the greater-than operator).
\item We could change the definition of the parallel combinators
  and define separate lexical tokens for the combinators, e.g.,
  \syncon{token Seq = ">[[:lower:]][[:word:]]*>"}. This would add
  just enough whitespace sensitivity to allow separating the
  different cases.
\item We could change the syntax of the combinators completely to
  avoid clashes with other operators.
\end{itemize}

The change in the first alternative can be done after composition,
and would allow us to reuse both language definitions without
modifications. In the latter two alternatives, we lose reuse of
the definitions of Orc combinators, but place no additional
restrictions on the base language. The preferred resolution
strategy is likely to differ between different compositions and
different languages.
%
For example, another unresolvable ambiguity is going to show up if
the base language uses semi-colons, e.g. for sequencing
expressions (this would clash with the ``otherwise'' combinator).
In this case, there is no reasonable way to disambiguate
``\ocaml{e1; e2}'' without changing the syntax of one of the
operations.
